---
title: "Payment and Coding Report (Pilot version)"
author: "Melissa Kline"
date: "12/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
```

# Session and payment tracking

This document is for tracking progress on the Physics study! It shows how many sessions have been completed for the Physics study, and whether or not participants have:

- Been coded for each session (and how many times)
- Been paid for each session
- Received their movie grid (the answer is yes for pilot!)
- Received their report (the answer is <UNKNOWN> for pilot!)

This version is for the pilot dataset, meaning it's retrospective only. However, it's built to use the standard datasets so should generalize relatively easy to the ongoing set. 

### Data read-in and merge

We read in from the 'live' data, i.e. the consent/account information generated by the lookit data processing python binaries.
```{r, echo = FALSE, results ='show', warning = FALSE}
accountsprod <- read.csv("/Users/mekline/Projects/LookitVideo_Old/accountsprod_583c892ec0d9d70082123d94.csv", stringsAsFactors = FALSE)
print("read in accountsprod_583c892ec0d9d70082123d94.csv")
sessions <- read.csv("/Users/mekline/Projects/LookitVideo_Old/583c892ec0d9d70082123d94_Kim.csv", stringsAsFactors = FALSE)
sessions2 <- read.csv("/Users/mekline/Projects/LookitVideo_Old/57bc591dc0d9d70055f775db_Kim.csv", stringsAsFactors = FALSE)

accountsprod <- accountsprod %>%
  select(username, name, email, okayToSend.personalCommunication, demographicsHowDidYouHear, demographicsLanguagesSpokenAtHome, name) %>%
  mutate(parent.firstName = name)

sessions <- sessions %>%
  select(shortId, username, child, child.firstName, child.gender, withdrawn, consent, usable, nVideosFound, allcoders, coded) %>%
  mutate(origin = '583c') %>%
  filter(consent == 'yes')

sessions2 <- sessions2 %>%
  select(shortId, username, child, child.firstName, child.gender, withdrawn, consent, usable, nVideosFound, allcoders, coded) %>%
  mutate(origin = '57bc') %>%
  filter(consent == 'yes')

sessions <- bind_rows(sessions, sessions2)

allInfo <- left_join(accountsprod, sessions, by=c('username'))
```


## Data Reports

We can now produce a summary for each participant - how many sessions they've done, and how many remain un-coded or un-paid.  Since there are some entries which are consented but consist only of the consent video, we'll follow that as well!

To start, everyone has been un-paid (This info isn't stored in the python object!!) Then, we make a csv that gets stored next to the report Rmd to keep track of results!

```{r, echo=FALSE, warning=FALSE}
summary <- allInfo %>%
  mutate(isOver1 = nVideosFound > 1) %>%
  mutate(nameIfNo = ifelse(coded == 'no', shortId, ''))%>%
  group_by(username, parent.firstName, child.firstName, email, okayToSend.personalCommunication) %>%
  dplyr::summarize(numEarnedSessions = n(), 
                   earnedBonus = numEarnedSessions > 11, 
                   numOver1 = sum(isOver1, na.rm = TRUE),
                   numUnCodedSessions = sum(coded == 'no', na.rm = TRUE),
                   namesUnCodedSessions = paste0(nameIfNo, collapse = ', '),
                   numPaidSessions = 0,
                   paidBonus = FALSE) %>%
  filter(numOver1 > 0) %>%
  mutate(moneyOwed = (numEarnedSessions)*5 + earnedBonus*5) %>%
  mutate(moneyPaid = (numPaidSessions)*5 + paidBonus*5) %>%
  select(username, moneyOwed, moneyPaid, child.firstName, email, everything())

#Now read in the tracker sheet and see if anything needs updated! (IE have we paid anyone since running this script last?)

payment_tracker = read.csv("payment_tracker.csv", stringsAsFactors = FALSE) %>%
  select(username, moneyOwed, moneyPaid, numEarnedSessions, earnedBonus)

summary <- left_join(summary, payment_tracker, by = 'username') 

summary <- summary %>%
  mutate(numPaidSessions = ifelse(moneyPaid.y > moneyPaid.x, numEarnedSessions.y, numPaidSessions)) %>%
  mutate(paidBonus = ifelse((moneyPaid.y > moneyPaid.x & earnedBonus.y == TRUE), TRUE, paidBonus)) %>%
  mutate(moneyPaid = moneyPaid.y) %>%
  mutate(numEarnedSessions = numEarnedSessions.x, 
         moneyOwed = moneyOwed.x - moneyPaid,
         earnedBonus = earnedBonus.x) %>%
  select(-contains('.x')) %>%
  select(-contains('.y')) %>%
  select(username, moneyOwed, moneyPaid, child.firstName, email, everything()) %>%
  ungroup()

          
#And write out the updated payment tracker
write.csv(select(summary, username,	moneyOwed,	moneyPaid,	child.firstName,	email, numEarnedSessions, earnedBonus),"payment_tracker.csv")

```

### Payment Report

Here is a list of payments left to be made. 

Please note! After you actually pay someone, you need to actually update that fact in the file `payment_tracker.csv` (i.e., updated the moneyPaid column to reflect what you've now paid the family!) before running this script again.

```{r, echo=FALSE, results='asis', warning=FALSE}
topay = summary %>%
  filter(numEarnedSessions > numPaidSessions)%>%
  select(username,	parent.firstName, moneyOwed,	child.firstName,	email, numEarnedSessions, numPaidSessions)
kable(topay)
```

Here are some emails you can send:
```{r, echo=FALSE, results='asis', warning=FALSE}

fiveEmails <- topay %>%
  head(3) %>%
  mutate(parent.nameToUse = ifelse(parent.firstName == "", username, parent.firstName))%>%
  mutate(emailTextNoBonus = paste("TO: ", email, "\nDear ", parent.nameToUse, ",\nThank you for participating in the 'Your Baby, the Physicist' study on Lookit! As a thank you, we are sending your family ", moneyOwed, "$ as a thank-you -- ", child.firstName, " completed a total of", numEarnedSessions-numPaidSessions, "sessions, for 5$ each.\nWe are sending this to you as an Amazon gift certificate. To access your gift certificate, you can go to [some website] and enter the following code, which is unique to you:\nsome code, hopefully procedurally generated!\nThank you again, and thank you so much for being a member of the Lookit community, \nMelissa at www.lookit.mit.edu"))%>%
  select(emailTextNoBonus)

kable(fiveEmails)
```


#### Coding Report

Here is a list of sessions that have been consented, but still need to be coded!
```{r, echo=FALSE, results='asis', warning=FALSE}
tocode = summary %>%
  filter(numUnCodedSessions > 0)%>%
  select(username, numUnCodedSessions, namesUnCodedSessions)
kable(tocode)
```